The paper on \Large \bf Blockchain Frontrunning

### 2018-09-10 frontrunning/Latex/sections/paper.tex
[frontrunning] More details added to domain frontrunning

%NOTE: @mahsa: is this considered a Historical evidence? should we talk about this somewhere else and maybe do a PoC on Ghazal for this section?
\subsubsection{Domain Name Front-running} \hfill\\    %Following section talks about front-running in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method)

%Jeremy's Comment: contrast ghazal vs ens, or try to have some historical evidence for namespace on the Ethereums. Try too make ghazal less central.
%Jeremy's comments: also talk about the "private information retrieval" (Ian Goldberg's work at waterloo)

\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not yet limited to the financial markets. Front-running can also occur within other (non-financial) blockchain applications such as naming systems. Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduces single point of failures in the entire web. Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \textit{.eth} domain names. These domains which can be resolved using any Ethereum web3 compatible browser. Although a sealed auction (\textit{startAuctionsAndBid}) is used while implementing the ENS, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount. By doing so the front-runner invalidates the original bid and hence registers the domain name himself.

Although the implementation uses a sealed auction, \textit{startAuctionsAndBid}, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount. By doing so the front-runner invalidates the original bid. This is similar to traditional domain squatting where the service provider maliciously buys the domains upon domain availably check and before the user gets the chance to finish his order. Although the exact same attack is not feasible on blockchain naming services as querying already registered domains are instant and without leaking any information of the intention of the user to the network.

One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}. Ghazal users rely on the Ethereum blockchain to register their \texttt{.ghazal} domain names and bind certificates to those names. In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument. As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block. During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user. In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user. A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees. This practice allows the adversarial party  to register an unregistered domain immediately after someone searched for it, and sell the domain name to the users for a higher price. Note that, domain name front-running also occurs in the vanilla system. In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.

%Some edits required here! @mahsa TODO

Ethereum Naming Service (ENS)\footnote{\url{https://ens.domains/}}, the most popular decentral naming service uses a sealed auction to purchase new domains with \textit{.eth} extension which can be resolved using any Ethereum web3 compatible browser. Although the implementation uses a sealed auction, \textit{startAuctionsAndBid}, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount. By doing so the front-runner invalidates the original bid. This is similar to traditional domain squatting where the service provider maliciously buys the domains upon domain availably check and before the user gets the chance to finish his order. Although the exact same attack is not feasible on blockchain naming services as querying already registered domains are instant and without leaking any information of the intention of the user to the network.
%e.g: https://etherscan.io/enslookup?q=handshaker.eth
%TODO: ian goberg: private information retrieval . talk about domain name frontrunning in the traditional sense and how goDaddy can steal the domain when queried for availablity. however in blockchain the queiry is private and does not reveal the intention that you want to buy the domain. View only / solidity code on how to enable this

>>>>

\subsubsection{Domain Name Front-running} \hfill\\

\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not yet limited to the financial markets. Front-running can also occur within other (non-financial) blockchain applications such as naming systems. Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduces single point of failures in the entire web. Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \texttt{.eth} domain names. These domains which can be resolved using any Ethereum web3 compatible browser. Although a sealed auction (\textit{startAuctionsAndBid}) is used while implementing the ENS, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount. By doing so the front-runner invalidates the original bid and hence registers the domain name himself. Ghazal is another Ethereum-based naming system that allows users to register \texttt{.ghazal} domain names and bind certificates to those names~\cite{moosavighazal}.  In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument. As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block. During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user. In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user. A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees. This practice allows the adversarial party  to register an unregistered domain immediately after someone searched for it, and sell the domain name to the users for a higher price. Note that, domain name front-running also occurs in the vanilla system. In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}. Front-running practice can happen in the traditional domain name system (DNS) as well. Domain name registrars can steal available domain names once seeing a query from users that looks up that domain's availability. In this case, the registrar can register the domain name ahead and sell it back to the user for a higher price.

%TODO: ian goberg: private information retrieval . talk about domain name frontrunning in the traditional sense and how goDaddy can steal the domain when queried for availablity. however in blockchain the queiry is private and does not reveal the intention that you want to buy the domain. View only / solidity code on how to enable this
